Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-05-03 results.tex
formatting tweak

For very large grid sizes the user can enable fast multipole method (FMM) assembly which internally is handled in Bempp-cl through an interface to the Exafmm-t FMM library. For $N$ surface elements this reduces the memory and computational complexity from $\mathcal{O}(N^2)$ in the dense assembly case to $\mathcal{O}(N)$ in the FMM case, making large boundary element problems tractable on standard workstations.

To couple FEniCSx with Bempp-cl we load a volume mesh with FEniCSx. We then export the corresponding boundary mesh into Bempp-cl and assemble the boundary spaces there. Bempp-cl provides numerical trace operators that can translate from the degree of freedom (DOF) representation in FEniCSx to the DOF representation in Bempp-cl. The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators. FMM assembly fits automatically into this framework and can be enabled or disabled as a simple configuration option.

Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment. The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl. \mscomment{I need to make this Bempp-cl release! A lot has changed since the 0.2.4 release}

>>>>

For very large grid sizes the user can enable fast multipole method (FMM) assembly which internally is handled in Bempp-cl through an interface to the Exafmm-t FMM library. For $N$ surface elements this reduces the memory and computational complexity from $\mathcal{O}(N^2)$ in the dense assembly case to $\mathcal{O}(N)$ in the FMM case, making large boundary element problems tractable on standard workstations. In this work, we only use the FMM in the performance analysis for larger structures, as all other cases are small enough to run efficiently with a dense assembler.

To couple FEniCSx with Bempp-cl we load a volume mesh with FEniCSx. We then export the corresponding boundary mesh into Bempp-cl and assemble the boundary spaces there. Bempp-cl provides numerical trace operators that can translate from the degree of freedom (DOF) representation in FEniCSx to the DOF representation in Bempp-cl. The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators. FMM assembly fits automatically into this framework and can be enabled or disabled as a simple configuration option.
Once the discrete block matrices in Eq.~\eqref{eq:fembem_matrix} are built with Bempp-cl and FEniCSx, we assemble them into one matrix and solve the linear system with Scipy's\cite{2020SciPy-NMeth} GMRES, in this case, with a tolerance of $10^{-5}$.

Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment. The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
